Hierarchical Reverberation Mapping

### 2013-12-03 Paper/ms.tex
More work on describing simulations

\section{Demonstration on Simulated Data}\label{sec:data}
To test our hierarchical model, and compare it to the stacked cross-correlation
function, we simulated data from a sample of 100 AGN. We assumed the
continuum flux for each object fluctuates around a mean value $m = 50$ in
arbitrary units. The variability timescales $L$ were simulated from a very
broad log-uniform distribution (i.e. a uniform distribution for $\ln(L)$)
with a lower limit of 100 days and an upper limit of $10,000$ days. The
variability amplitudes $\beta$ were also simulated from a log-uniform
distribution with lower limit of 0.2 flux units and an upper limit of 1 flux
unit. This implies some objects are more variable than others, as is typical
in reverberation mapping.

The measured data for each of the 100 AGN was
continuum flux measurements, once per day, for 100 days. The continuum fluxes
for each object oscillate around a mean value of 50 in arbitrary units, and the
standard deviation of the measurement noise is 1 (i.e. 2\%). The line data is measured on
only two days, with times selected from a uniform distribution between $t=50$
and $t=100$ days (i.e. corresponding to the latter half of the continuum data).
The flux of the line data is scaled to half that of the line data, and the
measurement noise for the line data is 0.25, or 1\%. See Figure~\ref{fig:data}
for three illustrative data sets from the sample.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{Figures/posterior.eps}
\caption{The joint posterior distribution for $\mu$ and $\sigma$, hyperparameters
describing the distribution of $\bar{\tau}$ values in the sample. The prior
distribution was uniform over the area shown.
The true solution $(\mu = 0.867, \sigma = 0.157)$
is indicated by the white star symbol.\label{fig:posterior}}
\end{center}
\end{figure}

@@

>>>>

\section{Demonstration on Simulated Data}\label{sec:data}
To test our hierarchical model, and compare it to the stacked cross-correlation
function, we simulated data from a sample of 100 AGN. We assumed the
continuum flux for each object fluctuates around a mean value $m = 50$ in
arbitrary units. The variability timescales $L$ were simulated from a very
broad log-uniform distribution (i.e. a uniform distribution for $\ln(L)$)
with a lower limit of 10 days and an upper limit of $1,000$ days. The
variability amplitudes $\beta$ were also simulated from a log-uniform
distribution with lower limit of 0.2 flux units and an upper limit of 1 flux
unit. This implies some objects are more variable than others, as is typical
in reverberation mapping.

Each object in the sample had its own transfer function parameters. The upper
limit $b$ of the transfer function was simulated using a log-normal distribution
with a median value of 10 days, and the standard deviation of $\ln(b)$ was
0.3. Given $b$, $a$ was simulated from a uniform distribution between $0$ and
$a$. The resulting distribution of lags $\bar{\tau} = (a+b)/2$ is very well
approximated by a lognormal distribution with a median of 7.4 days and width
(quantified by the standard deviation of $\log_{10}(\bar{\tau})$) of 0.157.
The response amplitudes $A$ and $C$ were set to 0.5 and 0 respectively, for
all objects.

The measured data for each of the 100 AGN was
continuum flux measurements, once per day, for 100 days. The continuum fluxes
for each object oscillate around a mean value of 50 in arbitrary units, and the
standard deviation of the measurement noise is 1 (i.e. 2\%). The line data is measured on
only two days, with times selected from a uniform distribution between $t=50$
and $t=100$ days (i.e. corresponding to the latter half of the continuum data).
The flux of the line data is typically about half that of the continuum data
(since $A=0.5$ for all objects), and the
measurement noise for the line data is 0.25, or about 1\%.
See Figure~\ref{fig:data} for three illustrative data sets from the sample.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{Figures/posterior.eps}
\caption{The joint posterior distribution for $\mu$ and $\sigma$, hyperparameters
describing the distribution of $\bar{\tau}$ values in the sample. The prior
distribution was uniform over the area shown.
The true solution $(\mu = 0.867, \sigma = 0.157)$
is indicated by the white star symbol. $\mu = 0.867$ corresponds to a typical
lag of 7.4 days.\label{fig:posterior}}
\end{center}
\end{figure}

@@

Note that our method for combining individual object results into an inference
about the population (Section~\ref{sec:multiple}) assumes that the hierarchical
prior applies to only a single parameter (in our case $\bar{\tau}$). If we
incorporate additional information by using a hierarchical prior for the other
model parameters, allowing us to detect (for example) that all of the response
amplitudes $A$ were equal to 0.5, we may be able to make more accurate
inferences. However, this would increase the complexity of the method and the
computational expense.
